---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = FALSE,
  asciicast_theme = "pkgdown"
)
asciicast::init_knitr_engine(
  startup = quote({
    library(sunsets)
    set.seed(1) }),
  echo = TRUE,
  echo_input = FALSE
)
```

# sunsets

<!-- badges: start -->
<!-- badges: end -->

Colour palettes inspired by sunsets in the Canadian Prairies.

The main purpose of sunsets is to serve as an example showing how to create a colour palette package with the **palettes** package. The palettes package provides a comprehensive library for colour vectors and colour palettes using a new family of colour classes (`palettes_colour`, and `palettes_palette`) that always print as hex codes with colour previews.

Colour palette packages created with palettes have access to the following capabilities, all without requiring you to write any code: formatting, casting and coercion, extraction and updating of components, plotting, colour mixing arithmetic, and colour interpolation. See the [Creating a colour palette package](https://mccarthy-m-g.github.io/palettes/articles/creating-packages.html) vignette in palettes for a step-by-step guide.

See the following vignettes to learn how to use sunsets' palettes with other packages:

- [Using palettes with ggplot2](https://mccarthy-m-g.github.io/palettes/articles/ggplot2.html)
- [Using palettes with gt](https://mccarthy-m-g.github.io/palettes/articles/gt.html)
- [Using palettes with biscale](https://mccarthy-m-g.github.io/palettes/articles/biscale.html)
- [Compatibility with other colour packages](https://mccarthy-m-g.github.io/palettes/articles/compatibility.html)

## Included palettes

```{r echo=FALSE, message=FALSE}
library(sunsets)
plot(sunset_palettes)
# Detaching so the loading message appears in the Usage section
detach("package:sunsets", unload=TRUE)
detach("package:palettes", unload=TRUE)
```

## Installation

You can install the development version of sunsets from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mccarthy-m-g/sunsets")
```

## Usage

```{r}
library(sunsets)
```

sunsets comes with a set of `r length(sunset_palettes_discrete)` discrete colour palettes, and `r length(sunset_palettes_sequential)` sequential colour palettes, which can be accessed from the following R objects:

- `sunset_palettes_discrete` for discrete palettes
- `sunset_palettes_sequential` for sequential palettes
- `sunset_palettes` for all palettes

To preview the palettes in the console simply print them:

```{asciicast sunset-palettes-discrete}
sunset_palettes_discrete
```

To preview the palettes in the Plots pane use `plot()`:

```{r plot-sunset-palettes-sequential}
plot(sunset_palettes_sequential)
```

To cast palettes to a tibble use `as_tibble()`:

```{asciicast as-tibble}
as_tibble(sunset_palettes)
```

Palettes can be subset using `[`, `[[`, and `$`.

  - To extract one or more palettes use `[`:

    ```{asciicast extract-palette}
    sunset_palettes_sequential[c("blue", "green")]
    ```
  
  - To extract a single palette as a colour vector use `[[` or `$`:

    ```{asciicast extract-vector-1}
    sunset_palettes_sequential[["purple"]]
    ```
    
    ```{asciicast extract-vector-2}
    sunset_palettes_sequential$purple
    ```
    
  - To get names of palettes use `names()`:

    ```{r}
    names(sunset_palettes_sequential)
    ```

## Documentation

See also documentation for the palettes package at [`https://mccarthy-m-g.github.io/palettes/`](https://mccarthy-m-g.github.io/palettes/reference/index.html) or in the installed package: `help(package = "palettes")`.

## License

CC0
